Scikit-learn: API design for machine learning

### 2013-06-18 paper.tex
put some stuff back in that I deleted by mistake

Initializing of estimator objects and actual learning are strictly separated,
in a way that is similar to partial function application:
an estimator is initialized from a set of hyper-parameter settings
(e.g., regularization parameters, random seeds)
and can be considered a function
that maps these settings to actual learning algorithms.
The object initializer does not see any actual data.
All it does is attach the given parameters to the object.
Hyper-parameter settings are public attributes
for the sake of convenient model inspection.

>>>>

Initializing of estimator objects and actual learning are strictly separated,
in a way that is similar to partial function application:
an estimator is initialized from a set of hyper-parameter settings
(e.g., regularization parameters, random seeds)
and can be considered a function
that maps these settings to actual learning algorithms.
The object initializer does not see any actual data.
All it does is attach the given parameters to the object.
Hyper-parameter settings are public attributes
for the sake of convenient model inspection,
which is especially important in model selection settings.
For ease of use, default hyper-parameter values are provided
for all built-in estimators.
These default values are set to be relevant in most common
situations in order to make estimators as effective as possible
\textit{out-of-box} for non-experts.
